---
title: "R markdown for presentations"
date: "`r Sys.Date()`"
author: "Austin Hart"
output:
  rmdformats::downcute:
    self_contained: true
    code_folding: show
    use_bookdown: true
    thumbnails: false
    default_style: "dark"
    downcute_theme: "default"
---


```{r setup, include=FALSE}
## Libraries
  library(knitr)
  library(rmdformats)

## Global options
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, prompt = FALSE,
  tidy = FALSE, comment = NA,
  message = FALSE, warning = FALSE
)
```

# Why bother with Markdown?

I taught myself `R Markdown` because I needed a better tool for creating presentations. I was sick of using `R` for my data work and a separate software and programming language for creating slides. The endless churn of exporting, moving, and changing visualizations was awful. So I started creating `ioslides`, `beamer`, and `xaringan` presentations in `R Markdown` instead. 

The `Markdown` world is perfect for the data analyst who has something to say. It lets you pull analysis and presentation into a single workflow, and it makes the task of updating, tweaking, and scaling your work a snap.

What I offer here is a very simple intro to two styles of presentation. There's so much more out there. [Yihui Xie's markdown book](https://bookdown.org/yihui/rmarkdown/) is an excellent starter kit.^[See especially Chapters 4, 7, and 9.] 

# ioslides presentations

`ioslides` offers the simplest space for creating presentations. Just specify `ioslides_presentation` output in the document `YAML`. Then define your `setup` chunk, and proceed to creating your slides.

## YAML options

The YAML metadata requires that you specify the output type. Here we have to say that we want slides:  `ioslides_presentation`. This will knit to an `html` document containing your presentation. Note that I also specify widescreen as the baseline. 

```yaml
---
title: "Presentations"
author: John Doe
date: 28 March 2023 
output: 
  ioslides_presentation:
    widescreen: true
---
```

## Setup chunk
Your 'setup' chunk is critical in every markdown document. This is where you specify what you want to happen with your code chunks when you `knit` the document. Of special importance for presentations, this is also a chance to set parameters for the visuals you create (size, resolution, graphics device, etc).

````r
`r ''````{r setup, include=F}
# Global options
  knitr::opts_chunk$set(
    echo = F, message = F, warning = F,
    fig.width = 4, fig.asp = 0.618, 
    fig.align = 'center', dev='png',
    out.width = "60%"
  )

# Packages
  library(tidyverse)
  library(kableExtra)
```
````

## Slide basics
The slide is the key "unit" of a presentation. In `ioslides`, level-1 headers, marked by `#`, become new section slides and `##` become new content slides.^[Note that only `#` and `##` headers initiate new slides. `###` headers and beyond just show up as text within a slide.]


```{r, eval=F, echo=T}
<!-- Basic slide structure -->

# Slide for first section

## Separate content slide

> A block quote. It's kind of like my motto.

- Starting a list  
- So many lists

## Another content slide 
### subtitle on the same slide

1. First step  

2. Second step
```

# xaringan presentations
I prefer `xaringan` for my presentations. `ioslides` is quick and easy, but the formatting options are very limited. `xaringan` has so many options for both the deck as a whole and individual slides.

## xaringan YAML
So many options here. Consider:

```yaml
---
title: "xaringan basics"
author: "Me me me"
institute: "Place I work"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, rladies, rladies-fonts]
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
---
```

I set the `libs` option so that my formatting files (related to the `css`options) don't clutter my directory.

Note that `xaringan` comes with loads of native `css` style options. The chunk above uses `rladies` theme and fonts. Explore the options to see what suits you.

## xaringan slides
With `xaringan`, use three dashes, `---`, to create new slides of any type. Note that slides also have classes to choose from. You can change light vs dark theme (inverse), vertical alignment (top, middle, bottom), and horizontal alignment (left, center, right).

```{r, eval=F, echo=T}
<!-- Xaringan structure after setup -->

## First slide doesn't need the `---`

- topics covered
- things you'll like

---
class: inverse, middle, right

# A different class!
### mess with the options

---
## Title of my new slide

.pull-left[
### pulled left
- divide into columns
- i'm on the left
]

.pull-right[
### pulled right
- other side
- greener here
]

---
# Second slide title

.left-column[
### First point
### Second point
### Finally
]

.right-column[
The .left- and .right-column options give you
more space with headers on the left-hand side 
to guide you through a single point.
]
```

# Other markdown stuff
A few quick reminders about `markdown` based on questions from the past week:  

- *Unique code chunk names*. You don't have to name your code chunks. If you do, they all need different names.  

- *Default working directory*. The folder containing your `.Rmd` file is your default directory when you `knit`. If your data and other materials are in the same spot, no need to `setwd`.  

- *`knitr` effectively runs its own R session*. Even if you attach `haven` in your console, for example, it won't be active when you `knit` a markdown document. I recommend loading these packages (and importing data) either in your setup chunk or in an invisible chunk immediately after it.

